---
title: "**Granja San Jose Report**"
output: html_document
params:
  all_data: 'NULL'
      
---

<style type = "text/css">

body{ /* Normal  */
      font-family: Helvetica;
      font-size: 12px;
      color: Grey;
        
  }
td {  /* Table  */
  font-family: Helvetica;
  font-size: 12px;
  text-align: center;
}
h1.title {
  font-family: Helvetica;
  font-size: 30px;
  color: #007582;
}
h1 { /* Header 1 */
  font-family: Helvetica;
  font-size: 24px;
  color: #007582;
  text-align: center;

}
h2 { /* Header 2 */
  font-family: Helvetica;
  font-size: 22px;
  color: #007582;
 
}
h3 { /* Header 3 */
  font-family: Helvetica;
  font-size: 22px;
  color: #007582;
  
}
code.r{ /* Code block */
    font-family: Helvetica;
    font-size: 12px;
}
pre { /* Code block - determines code spacing between lines */
    font-family: Helvetica;
    font-size: 14px;
}
</style>

<style>
.column-left{
  float: left;
  width: 50%;
  text-align: left;
}
.column-center{
  display: inline-block;
  width: 50%;
  text-align: center;
}

</style>

## 1 - Overall Statistics.

```{r, echo = FALSE, warning = FALSE, message = FALSE}

params$all_data |>
  dplyr::summarise(
    "No. Calves" = dplyr::n_distinct(CalfNumber),
    "Calf Age (days)" = mean(CalfAge, na.rm = TRUE),
    "Milk Cons. (l)" = mean(AverageConsumption, na.rm = TRUE),
    "Drink. Speed" = mean(AverageDrinkingSpeed, na.rm = TRUE),
    "Vis. With Cons." = mean(VisitsWithConsum, na.rm = TRUE),
    "Vis. With Credit Without Cons." = mean(VisitsWithCreditWithoutConsum, na.rm = TRUE),
    "Vis. Without Credit" = mean(VisitsWithoutCredit, na.rm = TRUE)) |> 
  dplyr::mutate(
          dplyr::across(dplyr::where(is.numeric), round, 2)
        ) |>
  kableExtra::kbl(row.names = FALSE, align = "l") |>
  kableExtra::column_spec(1, bold = TRUE) |>
  kableExtra::row_spec(0, bold = TRUE, color = "white", background = "#007582") |>
  kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))

```

## 2 - Overall Statistics Monthly. 

```{r, echo = FALSE, warning = FALSE, message = FALSE}

params$all_data |>
  dplyr::mutate(
    Month = lubridate::month(Day)
  ) |>
  dplyr::group_by(Month) |>
  dplyr::summarise(
    "No. Calves" = dplyr::n_distinct(CalfNumber),
    "Calf Age (days)" = mean(CalfAge, na.rm = TRUE),
    "Milk Cons. (l)" = mean(AverageConsumption, na.rm = TRUE),
    "Drink. Speed" = mean(AverageDrinkingSpeed, na.rm = TRUE),
    "Vis. With Cons." = mean(VisitsWithConsum, na.rm = TRUE),
    "Vis. With Credit Without Cons." = mean(VisitsWithCreditWithoutConsum, na.rm = TRUE),
    "Vis. Without Credit" = mean(VisitsWithoutCredit, na.rm = TRUE)) |> 
  dplyr::mutate(
    dplyr::across(dplyr::where(is.numeric), round, 2)) |>
  kableExtra::kbl(row.names = FALSE, align = "l") |>
  kableExtra::column_spec(1, bold = TRUE) |>
  kableExtra::row_spec(0, bold = TRUE, color = "white", background = "#007582") |>
  kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))

```

## 3 - Overall Statistics by Feeder. 

```{r, echo = FALSE, warning = FALSE, message = FALSE}

params$all_data |>
  dplyr::group_by(FeederNumber) |>
  dplyr::summarise(
    "No. Calves" = dplyr::n_distinct(CalfNumber),
    "Calf Age (days)" = mean(CalfAge, na.rm = TRUE),
    "Milk Cons. (l)" = mean(AverageConsumption, na.rm = TRUE),
    "Drink. Speed" = mean(AverageDrinkingSpeed, na.rm = TRUE),
    "Vis. With Cons." = mean(VisitsWithConsum, na.rm = TRUE),
    "Vis. With Credit Without Cons." = mean(VisitsWithCreditWithoutConsum, na.rm = TRUE),
    "Vis. Without Credit" = mean(VisitsWithoutCredit, na.rm = TRUE)) |> 
  dplyr::mutate(
    dplyr::across(dplyr::where(is.numeric), round, 2)) |>
  kableExtra::kbl(row.names = FALSE, align = "l") |>
  kableExtra::column_spec(1, bold = TRUE) |>
  kableExtra::row_spec(0, bold = TRUE, color = "white", background = "#007582") |>
  kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))

```

## 4 - All Variables by Feeder Over Time.

```{r, echo = FALSE, fig.width = 20, fig.height = 11, warning = FALSE, message = FALSE}

params$all_data |> 
  dplyr::select(-Iso, -LOM) |> 
  dplyr::mutate(
    Month = lubridate::month(Day)
  ) |> 
  dplyr::group_by(Day, FeederNumber) |> 
  dplyr::summarise(
    "No. obs." = dplyr::n(),
    "Calf Age (days)" = mean(CalfAge, na.rm = TRUE),
    "Milk Cons. (l)" = mean(AverageConsumption, na.rm = TRUE),
    "Drink. Speed" = mean(AverageDrinkingSpeed, na.rm = TRUE),
    "Vis. With Cons." = mean(VisitsWithConsum, na.rm = TRUE),
    "Vis. With Credit Without Cons." = mean(VisitsWithCreditWithoutConsum, na.rm = TRUE),
    "Vis. Without Credit" = mean(VisitsWithoutCredit, na.rm = TRUE)) |> 
  dplyr::mutate(
    dplyr::across(dplyr::where(is.numeric), round, 2)
  ) |>
  dplyr::ungroup() |>
  tidyr::pivot_longer(cols = -c(Day, FeederNumber),
                      names_to = "Variables",
                      values_to = "Values") |> 
  ggplot2::ggplot(ggplot2::aes(x = Day, y = Values, col = FeederNumber)) +
  ggplot2::geom_line() +
  ggplot2::geom_point() +
    ggplot2::facet_wrap(paste("Feeder:", FeederNumber)~Variables, scales = "free_y") +
  ggplot2::theme_bw() +
  ggplot2::theme(legend.position = "none")

```

## 5 - All Variables by Feeder Over Calf Age.

```{r, echo = FALSE, fig.width = 20, fig.height = 11, warning = FALSE, message = FALSE}

params$all_data |> 
  dplyr::select(-Iso, -LOM) |> 
  dplyr::group_by(CalfAge, FeederNumber) |> 
  dplyr::summarise(
    "No. obs." = dplyr::n(),
    "Milk Cons. (l)" = mean(AverageConsumption, na.rm = TRUE),
    "Drink. Speed" = mean(AverageDrinkingSpeed, na.rm = TRUE),
    "Vis. With Cons." = mean(VisitsWithConsum, na.rm = TRUE),
    "Vis. With Credit Without Cons." = mean(VisitsWithCreditWithoutConsum, na.rm = TRUE),
    "Vis. Without Credit" = mean(VisitsWithoutCredit, na.rm = TRUE)) |> 
  dplyr::mutate(
    dplyr::across(dplyr::where(is.numeric), round, 2)
  ) |>
  dplyr::ungroup() |>
  tidyr::pivot_longer(cols = -c(CalfAge, FeederNumber),
                      names_to = "Variables",
                      values_to = "Values") |> 
  ggplot2::ggplot(ggplot2::aes(x = CalfAge, y = Values, col = FeederNumber)) +
  ggplot2::geom_line() +
  ggplot2::geom_point() +
    ggplot2::facet_wrap(paste("Feeder:", FeederNumber)~Variables, scales = "free_y") +
  ggplot2::theme_bw() +
  ggplot2::theme(legend.position = "none")

```

<hr />
<p style = "text-align: center; color: #007582;"> All rights reserved - University of Vermont </p>
<center>

```{r, warning = FALSE, echo = FALSE}

path_logo <- system.file("app/www", "costaslablogo.jpeg", package = "GranjaSanJoseDashboard")

htmltools::img(
   src = knitr::image_uri(path_logo),
   style = "width:100px; height:85px;")
   
```
</center>
&nbsp;





